Rapid Cycleway Prioritisation Tool

### 2020-06-11 code/index.Rmd
Tweak text for index

The tool also identifies what a 'cohesive network' for cycling might look like if we were to consider a wider range of interventions such as closing roads to motorised traffic and creating one-way systems. This has been estimated by joining up roads that have a high cycling potential on some or all their length. The 'cohesive network' might help authorities considering area-wide interventions such as pedestrian and cycle zones or modal filters.

>>>>

The tool also identifies what a 'cohesive network' for cycling might look like if we were to consider a wider range of interventions such as closing roads to motorised traffic and creating one-way systems.
Unlike the 'top ranked new cycleways' layer, the cohesive network comprises all of the major high cycle potential corridors, including sections where the roads are narrower.

The layer was generated by joining up roads that have a high cycling potential on some or all their length. The 'cohesive network' might help authorities considering area-wide interventions such as pedestrian and cycle zones or modal filters.
